% Master test document for visual inspection of all paper figures.
% Compiles all 9 figures in sequence as a single PDF. Drop into NeurIPS
% style file by inputting individual \input{fig_*} files in the paper.
%
%   pdflatex figures_master.tex
%   pdflatex figures_master.tex  % twice for cross-references
%
\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{
  arrows.meta,
  positioning,
  shapes.geometric,
  decorations.pathreplacing,
  calc
}
\usepackage{caption}
\usepackage{booktabs}
\captionsetup{font=small, labelfont=bf}

\title{Discovery Tetrad — Paper Figures (Master Test File)}
\author{(authors redacted for double-blind review)}
\date{\today}

\begin{document}
\maketitle

\noindent This document compiles all 9 paper figures for visual inspection.
Each figure is also available as a standalone \texttt{.tex} fragment in
\texttt{paper/figures/}; the paper input order is:

\begin{enumerate}\itemsep0pt
  \item \texttt{fig\_substrate\_inheritance.tex} — \S 4 setup overview.
  \item \texttt{fig\_pipeline.tex} — \S 4 pipeline architecture.
  \item \texttt{fig\_tetrad\_arch.tex} — \S 3 four-gate two-layer architecture.
  \item \texttt{fig\_cell\_taxonomy.tex} — \S 3 25-cell verdict taxonomy.
  \item \texttt{fig\_cascade.tex} — \S 3 witness-layer cascade rule.
  \item \texttt{fig\_witness\_loop.tex} — \S 3 iterative re-evaluation.
  \item \texttt{fig\_goal\_witness\_failure.tex} — \S 1 case study (compreg).
  \item \texttt{fig\_sophism\_density.tex} — \S 5 headline result.
  \item \texttt{fig\_cell\_heatmap.tex} — \S 5 cell occupancy across substrates.
  \item \texttt{fig\_concordance.tex} — Appendix three-way concordance.
\end{enumerate}

\clearpage
\input{fig_substrate_inheritance.tex}
\input{fig_pipeline.tex}
\input{fig_tetrad_arch.tex}
\input{fig_cell_taxonomy.tex}
\input{fig_cascade.tex}
\input{fig_witness_loop.tex}
\input{fig_goal_witness_failure.tex}
\input{fig_sophism_density.tex}
\input{fig_cell_heatmap.tex}
\input{fig_concordance.tex}

\end{document}
